---
title: "uslides"
subtitle: "Example presentation"
date: "`r Sys.Date()`"
author: https://github.com/mkearney/uslides
institute: |
  | School of Journalism
  | Informatics Institute
  | University of Missouri
output: 
  uslides::uslides_html:
    self_contained: true
#output: uslides::uslides_pdf
---

```{r, setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, size = "\\scriptsize")
```

## uslides HTML presentation with R Markdown { .white }

Get it from GitHub: https://github.com/mkearney/uslides.

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Shower

These slides use a template from the [shower](https://github.com/shower/shower) presentation system. Notable features:

1. Works in all modern browsers
1. Presentation fully keyboard accessible
1. Multiple themes available
1. Printable to PDF

<p class="note"> Shower ['ʃəuə] noun. A person or thing that shows.</p>

## Two column layout

<p class="double">
What is it? Your fathers lightsaber. This is the weapon of a Jedi Knight. Not as clumsy or as random as a blaster. An elegant weapon for a more civilized time. For over a thousand generations the Jedi Knights were the guardians of peace and justice in the Old Republic. Before the dark times, before the Empire. How did my father die? A young Jedi named Darth Vader, who was a pupil of mine until he turned to evil, helped the Empire hunt down and destroy the Jedi Knights.
</p>


## Two column layout, independent columns

<div class="double">
<p class="double-flow">
How did I get into this mess? I really don't know how. We seem to be made to suffer.
</p><p class="double-flow">
It's our lot in life. I've got to rest before I fall apart.
</p>
</div>

## Lists

1. Simple lists are marked with bullets
1. Ordered lists begin with a number
1. You can even nest lists one inside another
    * Or mix their types
    * But do not go too far
    * Otherwise audience will be bored
1. Look, seven rows exactly!

## Formulas

Formulas are rendered by KaTeX, https://github.com/Khan/KaTeX

It supports both inline: \(y = x / 2\) and displayed formulas:

\[ x_{1,2} = \frac{- b \pm \sqrt{b^2 - 4ac}}{2a} \]

## Slide with quote

> Learning more about programming is a long-term investment: it won’t pay off immediately, but in the long term it will allow you to solve new problems more quickly, and let you reuse your insights from previous problems in new scenarios.

**-Hadley Wickham**

## Slide with R Code and Output

```{r, include=FALSE}
if (!requireNamespace("rtweet", quietly = TRUE)) install.packages("rtweet")
```
- Some text
```{r, cache=FALSE}
#hw <- rtweet::search_tweets("rstats")
mtcars
```

## Tables

|                   |  mpg  |  cyl  |  disp  |  hp  |
|:-----------------:|:-----:|:-----:|:------:|:----:|
|     Mazda RX4     | 21    |   6   |  160   | 110  |
|   Mazda RX4 Wag   | 21    |   6   |  160   | 110  |
|    Datsun 710     | 22.8  |   4   |  108   |  93  |
|   Hornet 4 Drive  | 21.4  |   6   |  258   | 110  |
| Hornet Sportabout | 18.7  |   8   |  360.0 | 175  |
|       Valiant     | 18.1  |   6   |  225.0 | 105  |
|      Duster 360   | 14.3  |   8   |  360.0 | 245  |

# Title slide

## Lists item by item

> 1. Lets you reveal list items one by one
> 2. To keep some key points
> 3. In secret from audience
> 4. But it will work only once
> 5. Nobody wants to see the same joke twice

## Slide with Plot

```{r, echo=FALSE, dev='jpeg'}
par(mar = c(5, 4, 1, 2) + 0.1)
pairs(iris[1:4], pch = 21,
      bg = c("red", "green3", "blue")[unclass(iris$Species)])
```
